w---
title: "Heat_Maps_Dream_Team"
author: "Minjie Xia, David Jeong, Alex Huo, Ignat Kulinka, Tim Yang"
date: "2017/4/28"
output:
  html_document: default
  pdf_document: default
---
```{r,echo=FALSE}
## PF: Channing Frye, Kevin Love
## C: Timofey Mozgov, Tristan Thompson
## SG: Iman Shumpert, J.R. Smith
## PG: Kyrie Irving, Matthew Dellavedova
## SF: LeBron James, Richard Jefferson
library(tidyverse)
library(readr)
library(stringr)
library(tidyr)
library(SportsAnalytics)
## truncatedss<-read_csv("~/Desktop/SPRING 2017/Academics/STATS 199/Data Sets/truncatedss1415.csv")
## truncatedss<-read_csv("~/Desktop/SPRING 2017/Academics/STATS 199/Data Sets/truncatedss1516.csv")
## truncatedss<-read_csv("~/Desktop/SPRING 2017/Academics/STATS 199/Data Sets/ss.csv")
## X1415plusranking <- read_csv("~/Desktop/SPRING 2017/Academics/STATS 199/Data Sets/1415plusranking.csv")
## X1516plusranking <- read_csv("~/Desktop/SPRING 2017/Academics/STATS 199/Data Sets/1516plusranking.csv")
finals <- read_csv("~/Desktop/Final Report/Final_nbadat.csv")
```
# For Channing Frye (PF)
```{r,echo = FALSE}
frye<-filter(finals,player=="Channing Frye")

density_made<-matrix(nrow=47,ncol=50)
density_missed<-matrix(nrow=47,ncol=50)
density_pctg<-matrix(nrow=47,ncol=50)

for(i in -25:24){
  square_feet_x<-filter(frye,converted_x>i & converted_x<=i+1)
  ## subset(frye,(converted_x>-25 & converted_x<=-24))
  for(j in -47:-1){
    square_feet<-filter(square_feet_x,converted_y>j & converted_y<=j+1)
    ## subset (square_feet_x,(converted_y>-47 & converted_y<=-46))
    a<-nrow(subset(square_feet,square_feet$result=="made"))
    density_made[j+48,i+26]<-a
    b<-nrow(subset(square_feet,square_feet$result=="missed"))
    density_missed[j+48,i+26]<-b
    density_pctg[j+48,i+26]<-a/(a+b)
  }
}
## density_made
dma<-as.data.frame(density_made)
colnames(dma)<-seq(from=-24.5,to=24.5,by=1)
rownames(dma)<-seq(from=-46.5,to=-0.5,by=1)
dma<-as.matrix(dma)
## density_missed
dmi<-as.data.frame(density_missed)
colnames(dmi)<-seq(from=-24.5,to=24.5,by=1)
rownames(dmi)<-seq(from=-46.5,to=-0.5,by=1)
dmi<-as.matrix(dmi)
## density_percentage
dpctg<-as.data.frame(density_pctg)
colnames(dpctg)<-seq(from=-24.5,to=24.5,by=1)
rownames(dpctg)<-seq(from=-46.5,to=-0.5,by=1)
dpctg<-as.matrix(dpctg)
```
## On 1*1 grids
```{r,echo = FALSE}
dpctgdf<-as.data.frame(dpctg)
frye12<-dpctgdf
frye12$converted_y<-rownames(frye12)
frye123<-gather(frye12,"converted_x","PCTG",1:50)
frye123[,c(1,2)]<-frye123[,c(2,1)]
colnames(frye123)<-colnames(frye123[c(2,1,3)])
frye123<-as.data.frame(frye123)
frye1234<-filter(frye123,is.nan(PCTG)==FALSE)
frye1234$converted_x<-as.numeric(frye1234$converted_x) # With correction
frye1234$converted_y<-as.numeric(frye1234$converted_y) # With correction
frye1234$PCTG<-as.numeric(frye1234$PCTG)


dmidf<-as.data.frame(dmi)
frye22<-dmidf
frye22$converted_y<-rownames(frye22)
frye223<-gather(frye22,"converted_x","nmissed",1:50)
frye2234<-merge(frye1234,frye223,by=c("converted_x","converted_y"))

dmadf<-as.data.frame(dma)
frye32<-dmadf
frye32$converted_y<-rownames(frye32)
frye323<-gather(frye32,"converted_x","nmade",1:50)
frye3234<-merge(frye2234,frye323,by=c("converted_x","converted_y"))
frye3234$Shots<-frye3234$nmade+frye3234$nmissed
frye3234$nnormalized<-frye3234$Shots/max(frye3234$Shots)
frye3234$Distance<-sqrt((frye3234$converted_x)^2+(frye3234$converted_y+41.75)^2)
frye3234$Name<-"Channing Frye"
frye3234$Position<-"PF"
```
# For Kevin Love (PF)
```{r,echo = FALSE}
love<-filter(finals,player=="Kevin Love")
density_made<-matrix(nrow=47,ncol=50)
density_missed<-matrix(nrow=47,ncol=50)
density_pctg<-matrix(nrow=47,ncol=50)

for(i in -25:24){
  square_feet_x<-filter(love,converted_x>i & converted_x<=i+1)
  ## subset(love,(converted_x>-25 & converted_x<=-24))
  for(j in -47:-1){
    square_feet<-filter(square_feet_x,converted_y>j & converted_y<=j+1)
    ## subset (square_feet_x,(converted_y>-47 & converted_y<=-46))
    a<-nrow(subset(square_feet,square_feet$result=="made"))
    density_made[j+48,i+26]<-a
    b<-nrow(subset(square_feet,square_feet$result=="missed"))
    density_missed[j+48,i+26]<-b
    density_pctg[j+48,i+26]<-a/(a+b)
  }
}
## density_made
dma<-as.data.frame(density_made)
colnames(dma)<-seq(from=-24.5,to=24.5,by=1)
rownames(dma)<-seq(from=-46.5,to=-0.5,by=1)
dma<-as.matrix(dma)
## density_missed
dmi<-as.data.frame(density_missed)
colnames(dmi)<-seq(from=-24.5,to=24.5,by=1)
rownames(dmi)<-seq(from=-46.5,to=-0.5,by=1)
dmi<-as.matrix(dmi)
## density_percentage
dpctg<-as.data.frame(density_pctg)
colnames(dpctg)<-seq(from=-24.5,to=24.5,by=1)
rownames(dpctg)<-seq(from=-46.5,to=-0.5,by=1)
dpctg<-as.matrix(dpctg)
```
## On 1*1 grids
```{r,echo = FALSE}
dpctgdf<-as.data.frame(dpctg)
love12<-dpctgdf
love12$converted_y<-rownames(love12)
love123<-gather(love12,"converted_x","PCTG",1:50)
love123[,c(1,2)]<-love123[,c(2,1)]
colnames(love123)<-colnames(love123[c(2,1,3)])
love123<-as.data.frame(love123)
love1234<-filter(love123,is.nan(PCTG)==FALSE)
love1234$converted_x<-as.numeric(love1234$converted_x) # With correction
love1234$converted_y<-as.numeric(love1234$converted_y) # With correction
love1234$PCTG<-as.numeric(love1234$PCTG)


dmidf<-as.data.frame(dmi)
love22<-dmidf
love22$converted_y<-rownames(love22)
love223<-gather(love22,"converted_x","nmissed",1:50)
love2234<-merge(love1234,love223,by=c("converted_x","converted_y"))

dmadf<-as.data.frame(dma)
love32<-dmadf
love32$converted_y<-rownames(love32)
love323<-gather(love32,"converted_x","nmade",1:50)
love3234<-merge(love2234,love323,by=c("converted_x","converted_y"))
love3234$Shots<-love3234$nmade+love3234$nmissed
love3234$nnormalized<-love3234$Shots/max(love3234$Shots)
love3234$Distance<-sqrt((love3234$converted_x)^2+(love3234$converted_y+41.75)^2)
love3234$Name<-"Kevin Love"
love3234$Position<-"PF"
```
## For Timofey Mozgov (C)
```{r,echo = FALSE}
mozgov<-filter(finals,player=="Timofey Mozgov")
density_made<-matrix(nrow=47,ncol=50)
density_missed<-matrix(nrow=47,ncol=50)
density_pctg<-matrix(nrow=47,ncol=50)

for(i in -25:24){
  square_feet_x<-filter(mozgov,converted_x>i & converted_x<=i+1)
  ## subset(mozgov,(converted_x>-25 & converted_x<=-24))
  for(j in -47:-1){
    square_feet<-filter(square_feet_x,converted_y>j & converted_y<=j+1)
    ## subset (square_feet_x,(converted_y>-47 & converted_y<=-46))
    a<-nrow(subset(square_feet,square_feet$result=="made"))
    density_made[j+48,i+26]<-a
    b<-nrow(subset(square_feet,square_feet$result=="missed"))
    density_missed[j+48,i+26]<-b
    density_pctg[j+48,i+26]<-a/(a+b)
  }
}
## density_made
dma<-as.data.frame(density_made)
colnames(dma)<-seq(from=-24.5,to=24.5,by=1)
rownames(dma)<-seq(from=-46.5,to=-0.5,by=1)
dma<-as.matrix(dma)
## density_missed
dmi<-as.data.frame(density_missed)
colnames(dmi)<-seq(from=-24.5,to=24.5,by=1)
rownames(dmi)<-seq(from=-46.5,to=-0.5,by=1)
dmi<-as.matrix(dmi)
## density_percentage
dpctg<-as.data.frame(density_pctg)
colnames(dpctg)<-seq(from=-24.5,to=24.5,by=1)
rownames(dpctg)<-seq(from=-46.5,to=-0.5,by=1)
dpctg<-as.matrix(dpctg)
```
## On 1*1 grids
```{r,echo = FALSE}
dpctgdf<-as.data.frame(dpctg)
mozgov12<-dpctgdf
mozgov12$converted_y<-rownames(mozgov12)
mozgov123<-gather(mozgov12,"converted_x","PCTG",1:50)
mozgov123[,c(1,2)]<-mozgov123[,c(2,1)]
colnames(mozgov123)<-colnames(mozgov123[c(2,1,3)])
mozgov123<-as.data.frame(mozgov123)
mozgov1234<-filter(mozgov123,is.nan(PCTG)==FALSE)
mozgov1234$converted_x<-as.numeric(mozgov1234$converted_x) # With correction
mozgov1234$converted_y<-as.numeric(mozgov1234$converted_y) # With correction
mozgov1234$PCTG<-as.numeric(mozgov1234$PCTG)


dmidf<-as.data.frame(dmi)
mozgov22<-dmidf
mozgov22$converted_y<-rownames(mozgov22)
mozgov223<-gather(mozgov22,"converted_x","nmissed",1:50)
mozgov2234<-merge(mozgov1234,mozgov223,by=c("converted_x","converted_y"))

dmadf<-as.data.frame(dma)
mozgov32<-dmadf
mozgov32$converted_y<-rownames(mozgov32)
mozgov323<-gather(mozgov32,"converted_x","nmade",1:50)
mozgov3234<-merge(mozgov2234,mozgov323,by=c("converted_x","converted_y"))
mozgov3234$Shots<-mozgov3234$nmade+mozgov3234$nmissed
mozgov3234$nnormalized<-mozgov3234$Shots/max(mozgov3234$Shots)
mozgov3234$Distance<-sqrt((mozgov3234$converted_x)^2+(mozgov3234$converted_y+41.75)^2)
mozgov3234$Name<-"Timofey Mozgov"
mozgov3234$Position<-"C"
```
## For Tristan Thompson (C)
```{r,echo = FALSE}
thompson<-filter(finals,player=="Tristan Thompson")
density_made<-matrix(nrow=47,ncol=50)
density_missed<-matrix(nrow=47,ncol=50)
density_pctg<-matrix(nrow=47,ncol=50)

for(i in -25:24){
  square_feet_x<-filter(thompson,converted_x>i & converted_x<=i+1)
  ## subset(thompson,(converted_x>-25 & converted_x<=-24))
  for(j in -47:-1){
    square_feet<-filter(square_feet_x,converted_y>j & converted_y<=j+1)
    ## subset (square_feet_x,(converted_y>-47 & converted_y<=-46))
    a<-nrow(subset(square_feet,square_feet$result=="made"))
    density_made[j+48,i+26]<-a
    b<-nrow(subset(square_feet,square_feet$result=="missed"))
    density_missed[j+48,i+26]<-b
    density_pctg[j+48,i+26]<-a/(a+b)
  }
}
## density_made
dma<-as.data.frame(density_made)
colnames(dma)<-seq(from=-24.5,to=24.5,by=1)
rownames(dma)<-seq(from=-46.5,to=-0.5,by=1)
dma<-as.matrix(dma)
## density_missed
dmi<-as.data.frame(density_missed)
colnames(dmi)<-seq(from=-24.5,to=24.5,by=1)
rownames(dmi)<-seq(from=-46.5,to=-0.5,by=1)
dmi<-as.matrix(dmi)
## density_percentage
dpctg<-as.data.frame(density_pctg)
colnames(dpctg)<-seq(from=-24.5,to=24.5,by=1)
rownames(dpctg)<-seq(from=-46.5,to=-0.5,by=1)
dpctg<-as.matrix(dpctg)
```
## On 1*1 grids
```{r,echo = FALSE}
dpctgdf<-as.data.frame(dpctg)
thompson12<-dpctgdf
thompson12$converted_y<-rownames(thompson12)
thompson123<-gather(thompson12,"converted_x","PCTG",1:50)
thompson123[,c(1,2)]<-thompson123[,c(2,1)]
colnames(thompson123)<-colnames(thompson123[c(2,1,3)])
thompson123<-as.data.frame(thompson123)
thompson1234<-filter(thompson123,is.nan(PCTG)==FALSE)
thompson1234$converted_x<-as.numeric(thompson1234$converted_x) # With correction
thompson1234$converted_y<-as.numeric(thompson1234$converted_y) # With correction
thompson1234$PCTG<-as.numeric(thompson1234$PCTG)


dmidf<-as.data.frame(dmi)
thompson22<-dmidf
thompson22$converted_y<-rownames(thompson22)
thompson223<-gather(thompson22,"converted_x","nmissed",1:50)
thompson2234<-merge(thompson1234,thompson223,by=c("converted_x","converted_y"))

dmadf<-as.data.frame(dma)
thompson32<-dmadf
thompson32$converted_y<-rownames(thompson32)
thompson323<-gather(thompson32,"converted_x","nmade",1:50)
thompson3234<-merge(thompson2234,thompson323,by=c("converted_x","converted_y"))
thompson3234$Shots<-thompson3234$nmade+thompson3234$nmissed
thompson3234$nnormalized<-thompson3234$Shots/max(thompson3234$Shots)
thompson3234$Distance<-sqrt((thompson3234$converted_x)^2+(thompson3234$converted_y+41.75)^2)
thompson3234$Name<-"Tristan Thompson"
thompson3234$Position<-"C"
```
# For J.R. Smith (SG)
```{r,echo = FALSE}
smith<-filter(finals,player=="J.R. Smith")

density_made<-matrix(nrow=47,ncol=50)
density_missed<-matrix(nrow=47,ncol=50)
density_pctg<-matrix(nrow=47,ncol=50)

for(i in -25:24){
  square_feet_x<-filter(smith,converted_x>i & converted_x<=i+1)
  ## subset(smith,(converted_x>-25 & converted_x<=-24))
  for(j in -47:-1){
    square_feet<-filter(square_feet_x,converted_y>j & converted_y<=j+1)
    ## subset (square_feet_x,(converted_y>-47 & converted_y<=-46))
    a<-nrow(subset(square_feet,square_feet$result=="made"))
    density_made[j+48,i+26]<-a
    b<-nrow(subset(square_feet,square_feet$result=="missed"))
    density_missed[j+48,i+26]<-b
    density_pctg[j+48,i+26]<-a/(a+b)
  }
}
## density_made
dma<-as.data.frame(density_made)
colnames(dma)<-seq(from=-24.5,to=24.5,by=1)
rownames(dma)<-seq(from=-46.5,to=-0.5,by=1)
dma<-as.matrix(dma)
## density_missed
dmi<-as.data.frame(density_missed)
colnames(dmi)<-seq(from=-24.5,to=24.5,by=1)
rownames(dmi)<-seq(from=-46.5,to=-0.5,by=1)
dmi<-as.matrix(dmi)
## density_percentage
dpctg<-as.data.frame(density_pctg)
colnames(dpctg)<-seq(from=-24.5,to=24.5,by=1)
rownames(dpctg)<-seq(from=-46.5,to=-0.5,by=1)
dpctg<-as.matrix(dpctg)
```
## On 1*1 grids
```{r,echo = FALSE}
dpctgdf<-as.data.frame(dpctg)
smith12<-dpctgdf
smith12$converted_y<-rownames(smith12)
smith123<-gather(smith12,"converted_x","PCTG",1:50)
smith123[,c(1,2)]<-smith123[,c(2,1)]
colnames(smith123)<-colnames(smith123[c(2,1,3)])
smith123<-as.data.frame(smith123)
smith1234<-filter(smith123,is.nan(PCTG)==FALSE)
smith1234$converted_x<-as.numeric(smith1234$converted_x) # With correction
smith1234$converted_y<-as.numeric(smith1234$converted_y) # With correction
smith1234$PCTG<-as.numeric(smith1234$PCTG)


dmidf<-as.data.frame(dmi)
smith22<-dmidf
smith22$converted_y<-rownames(smith22)
smith223<-gather(smith22,"converted_x","nmissed",1:50)
smith2234<-merge(smith1234,smith223,by=c("converted_x","converted_y"))

dmadf<-as.data.frame(dma)
smith32<-dmadf
smith32$converted_y<-rownames(smith32)
smith323<-gather(smith32,"converted_x","nmade",1:50)
smith3234<-merge(smith2234,smith323,by=c("converted_x","converted_y"))
smith3234$Shots<-smith3234$nmade+smith3234$nmissed
smith3234$nnormalized<-smith3234$Shots/max(smith3234$Shots)
smith3234$Distance<-sqrt((smith3234$converted_x)^2+(smith3234$converted_y+41.75)^2)
smith3234$Name<-"J.R. Smith"
smith3234$Position<-"SG"
```
# For Iman Shumpert (SG)
```{r,echo = FALSE}
shumpert<-filter(finals,player=="Iman Shumpert")

density_made<-matrix(nrow=47,ncol=50)
density_missed<-matrix(nrow=47,ncol=50)
density_pctg<-matrix(nrow=47,ncol=50)

for(i in -25:24){
  square_feet_x<-filter(shumpert,converted_x>i & converted_x<=i+1)
  ## subset(shumpert,(converted_x>-25 & converted_x<=-24))
  for(j in -47:-1){
    square_feet<-filter(square_feet_x,converted_y>j & converted_y<=j+1)
    ## subset (square_feet_x,(converted_y>-47 & converted_y<=-46))
    a<-nrow(subset(square_feet,square_feet$result=="made"))
    density_made[j+48,i+26]<-a
    b<-nrow(subset(square_feet,square_feet$result=="missed"))
    density_missed[j+48,i+26]<-b
    density_pctg[j+48,i+26]<-a/(a+b)
  }
}
## density_made
dma<-as.data.frame(density_made)
colnames(dma)<-seq(from=-24.5,to=24.5,by=1)
rownames(dma)<-seq(from=-46.5,to=-0.5,by=1)
dma<-as.matrix(dma)
## density_missed
dmi<-as.data.frame(density_missed)
colnames(dmi)<-seq(from=-24.5,to=24.5,by=1)
rownames(dmi)<-seq(from=-46.5,to=-0.5,by=1)
dmi<-as.matrix(dmi)
## density_percentage
dpctg<-as.data.frame(density_pctg)
colnames(dpctg)<-seq(from=-24.5,to=24.5,by=1)
rownames(dpctg)<-seq(from=-46.5,to=-0.5,by=1)
dpctg<-as.matrix(dpctg)
```
## On 1*1 grids
```{r,echo = FALSE}
dpctgdf<-as.data.frame(dpctg)
shumpert12<-dpctgdf
shumpert12$converted_y<-rownames(shumpert12)
shumpert123<-gather(shumpert12,"converted_x","PCTG",1:50)
shumpert123[,c(1,2)]<-shumpert123[,c(2,1)]
colnames(shumpert123)<-colnames(shumpert123[c(2,1,3)])
shumpert123<-as.data.frame(shumpert123)
shumpert1234<-filter(shumpert123,is.nan(PCTG)==FALSE)
shumpert1234$converted_x<-as.numeric(shumpert1234$converted_x) # With correction
shumpert1234$converted_y<-as.numeric(shumpert1234$converted_y) # With correction
shumpert1234$PCTG<-as.numeric(shumpert1234$PCTG)


dmidf<-as.data.frame(dmi)
shumpert22<-dmidf
shumpert22$converted_y<-rownames(shumpert22)
shumpert223<-gather(shumpert22,"converted_x","nmissed",1:50)
shumpert2234<-merge(shumpert1234,shumpert223,by=c("converted_x","converted_y"))

dmadf<-as.data.frame(dma)
shumpert32<-dmadf
shumpert32$converted_y<-rownames(shumpert32)
shumpert323<-gather(shumpert32,"converted_x","nmade",1:50)
shumpert3234<-merge(shumpert2234,shumpert323,by=c("converted_x","converted_y"))
shumpert3234$Shots<-shumpert3234$nmade+shumpert3234$nmissed
shumpert3234$nnormalized<-shumpert3234$Shots/max(shumpert3234$Shots)
shumpert3234$Distance<-sqrt((shumpert3234$converted_x)^2+(shumpert3234$converted_y+41.75)^2)
shumpert3234$Name<-"Iman Shumpert"
shumpert3234$Position<-"SG"
```
# For Kyrie Irving (PG)
```{r,echo = FALSE}
irving<-filter(finals,player=="Kyrie Irving")

density_made<-matrix(nrow=47,ncol=50)
density_missed<-matrix(nrow=47,ncol=50)
density_pctg<-matrix(nrow=47,ncol=50)

for(i in -25:24){
  square_feet_x<-filter(irving,converted_x>i & converted_x<=i+1)
  ## subset(irving,(converted_x>-25 & converted_x<=-24))
  for(j in -47:-1){
    square_feet<-filter(square_feet_x,converted_y>j & converted_y<=j+1)
    ## subset (square_feet_x,(converted_y>-47 & converted_y<=-46))
    a<-nrow(subset(square_feet,square_feet$result=="made"))
    density_made[j+48,i+26]<-a
    b<-nrow(subset(square_feet,square_feet$result=="missed"))
    density_missed[j+48,i+26]<-b
    density_pctg[j+48,i+26]<-a/(a+b)
  }
}
## density_made
dma<-as.data.frame(density_made)
colnames(dma)<-seq(from=-24.5,to=24.5,by=1)
rownames(dma)<-seq(from=-46.5,to=-0.5,by=1)
dma<-as.matrix(dma)
## density_missed
dmi<-as.data.frame(density_missed)
colnames(dmi)<-seq(from=-24.5,to=24.5,by=1)
rownames(dmi)<-seq(from=-46.5,to=-0.5,by=1)
dmi<-as.matrix(dmi)
## density_percentage
dpctg<-as.data.frame(density_pctg)
colnames(dpctg)<-seq(from=-24.5,to=24.5,by=1)
rownames(dpctg)<-seq(from=-46.5,to=-0.5,by=1)
dpctg<-as.matrix(dpctg)
```
## On 1*1 grids
```{r,echo = FALSE}
dpctgdf<-as.data.frame(dpctg)
irving12<-dpctgdf
irving12$converted_y<-rownames(irving12)
irving123<-gather(irving12,"converted_x","PCTG",1:50)
irving123[,c(1,2)]<-irving123[,c(2,1)]
colnames(irving123)<-colnames(irving123[c(2,1,3)])
irving123<-as.data.frame(irving123)
irving1234<-filter(irving123,is.nan(PCTG)==FALSE)
irving1234$converted_x<-as.numeric(irving1234$converted_x) # With correction
irving1234$converted_y<-as.numeric(irving1234$converted_y) # With correction
irving1234$PCTG<-as.numeric(irving1234$PCTG)


dmidf<-as.data.frame(dmi)
irving22<-dmidf
irving22$converted_y<-rownames(irving22)
irving223<-gather(irving22,"converted_x","nmissed",1:50)
irving2234<-merge(irving1234,irving223,by=c("converted_x","converted_y"))

dmadf<-as.data.frame(dma)
irving32<-dmadf
irving32$converted_y<-rownames(irving32)
irving323<-gather(irving32,"converted_x","nmade",1:50)
irving3234<-merge(irving2234,irving323,by=c("converted_x","converted_y"))
irving3234$Shots<-irving3234$nmade+irving3234$nmissed
irving3234$nnormalized<-irving3234$Shots/max(irving3234$Shots)
irving3234$Distance<-sqrt((irving3234$converted_x)^2+(irving3234$converted_y+41.75)^2)
irving3234$Name<-"Kyrie Irving"
irving3234$Position<-"PG"
```
# For Matthew Dellavedova (PG)
```{r,echo = FALSE}
dellavedova<-filter(finals,player=="Matthew Dellavedova")

density_made<-matrix(nrow=47,ncol=50)
density_missed<-matrix(nrow=47,ncol=50)
density_pctg<-matrix(nrow=47,ncol=50)

for(i in -25:24){
  square_feet_x<-filter(dellavedova,converted_x>i & converted_x<=i+1)
  ## subset(dellavedova,(converted_x>-25 & converted_x<=-24))
  for(j in -47:-1){
    square_feet<-filter(square_feet_x,converted_y>j & converted_y<=j+1)
    ## subset (square_feet_x,(converted_y>-47 & converted_y<=-46))
    a<-nrow(subset(square_feet,square_feet$result=="made"))
    density_made[j+48,i+26]<-a
    b<-nrow(subset(square_feet,square_feet$result=="missed"))
    density_missed[j+48,i+26]<-b
    density_pctg[j+48,i+26]<-a/(a+b)
  }
}
## density_made
dma<-as.data.frame(density_made)
colnames(dma)<-seq(from=-24.5,to=24.5,by=1)
rownames(dma)<-seq(from=-46.5,to=-0.5,by=1)
dma<-as.matrix(dma)
## density_missed
dmi<-as.data.frame(density_missed)
colnames(dmi)<-seq(from=-24.5,to=24.5,by=1)
rownames(dmi)<-seq(from=-46.5,to=-0.5,by=1)
dmi<-as.matrix(dmi)
## density_percentage
dpctg<-as.data.frame(density_pctg)
colnames(dpctg)<-seq(from=-24.5,to=24.5,by=1)
rownames(dpctg)<-seq(from=-46.5,to=-0.5,by=1)
dpctg<-as.matrix(dpctg)
```
## On 1*1 grids
```{r,echo = FALSE}
dpctgdf<-as.data.frame(dpctg)
dellavedova12<-dpctgdf
dellavedova12$converted_y<-rownames(dellavedova12)
dellavedova123<-gather(dellavedova12,"converted_x","PCTG",1:50)
dellavedova123[,c(1,2)]<-dellavedova123[,c(2,1)]
colnames(dellavedova123)<-colnames(dellavedova123[c(2,1,3)])
dellavedova123<-as.data.frame(dellavedova123)
dellavedova1234<-filter(dellavedova123,is.nan(PCTG)==FALSE)
dellavedova1234$converted_x<-as.numeric(dellavedova1234$converted_x) # With correction
dellavedova1234$converted_y<-as.numeric(dellavedova1234$converted_y) # With correction
dellavedova1234$PCTG<-as.numeric(dellavedova1234$PCTG)


dmidf<-as.data.frame(dmi)
dellavedova22<-dmidf
dellavedova22$converted_y<-rownames(dellavedova22)
dellavedova223<-gather(dellavedova22,"converted_x","nmissed",1:50)
dellavedova2234<-merge(dellavedova1234,dellavedova223,by=c("converted_x","converted_y"))

dmadf<-as.data.frame(dma)
dellavedova32<-dmadf
dellavedova32$converted_y<-rownames(dellavedova32)
dellavedova323<-gather(dellavedova32,"converted_x","nmade",1:50)
dellavedova3234<-merge(dellavedova2234,dellavedova323,by=c("converted_x","converted_y"))
dellavedova3234$Shots<-dellavedova3234$nmade+dellavedova3234$nmissed
dellavedova3234$nnormalized<-dellavedova3234$Shots/max(dellavedova3234$Shots)
dellavedova3234$Distance<-sqrt((dellavedova3234$converted_x)^2+(dellavedova3234$converted_y+41.75)^2)
dellavedova3234$Name<-"Matthew Dellavedova"
dellavedova3234$Position<-"PG"
```
# For LeBron James (SF)
```{r,echo = FALSE}
james<-filter(finals,player=="LeBron James")

density_made<-matrix(nrow=47,ncol=50)
density_missed<-matrix(nrow=47,ncol=50)
density_pctg<-matrix(nrow=47,ncol=50)

for(i in -25:24){
  square_feet_x<-filter(james,converted_x>i & converted_x<=i+1)
  ## subset(james,(converted_x>-25 & converted_x<=-24))
  for(j in -47:-1){
    square_feet<-filter(square_feet_x,converted_y>j & converted_y<=j+1)
    ## subset (square_feet_x,(converted_y>-47 & converted_y<=-46))
    a<-nrow(subset(square_feet,square_feet$result=="made"))
    density_made[j+48,i+26]<-a
    b<-nrow(subset(square_feet,square_feet$result=="missed"))
    density_missed[j+48,i+26]<-b
    density_pctg[j+48,i+26]<-a/(a+b)
  }
}
## density_made
dma<-as.data.frame(density_made)
colnames(dma)<-seq(from=-24.5,to=24.5,by=1)
rownames(dma)<-seq(from=-46.5,to=-0.5,by=1)
dma<-as.matrix(dma)
## density_missed
dmi<-as.data.frame(density_missed)
colnames(dmi)<-seq(from=-24.5,to=24.5,by=1)
rownames(dmi)<-seq(from=-46.5,to=-0.5,by=1)
dmi<-as.matrix(dmi)
## density_percentage
dpctg<-as.data.frame(density_pctg)
colnames(dpctg)<-seq(from=-24.5,to=24.5,by=1)
rownames(dpctg)<-seq(from=-46.5,to=-0.5,by=1)
dpctg<-as.matrix(dpctg)
```
## On 1*1 grids
```{r,echo = FALSE}
dpctgdf<-as.data.frame(dpctg)
james12<-dpctgdf
james12$converted_y<-rownames(james12)
james123<-gather(james12,"converted_x","PCTG",1:50)
james123[,c(1,2)]<-james123[,c(2,1)]
colnames(james123)<-colnames(james123[c(2,1,3)])
james123<-as.data.frame(james123)
james1234<-filter(james123,is.nan(PCTG)==FALSE)
james1234$converted_x<-as.numeric(james1234$converted_x) # With correction
james1234$converted_y<-as.numeric(james1234$converted_y) # With correction
james1234$PCTG<-as.numeric(james1234$PCTG)


dmidf<-as.data.frame(dmi)
james22<-dmidf
james22$converted_y<-rownames(james22)
james223<-gather(james22,"converted_x","nmissed",1:50)
james2234<-merge(james1234,james223,by=c("converted_x","converted_y"))

dmadf<-as.data.frame(dma)
james32<-dmadf
james32$converted_y<-rownames(james32)
james323<-gather(james32,"converted_x","nmade",1:50)
james3234<-merge(james2234,james323,by=c("converted_x","converted_y"))
james3234$Shots<-james3234$nmade+james3234$nmissed
james3234$nnormalized<-james3234$Shots/max(james3234$Shots)
james3234$Distance<-sqrt((james3234$converted_x)^2+(james3234$converted_y+41.75)^2)
james3234$Name<-"LeBron James"
james3234$Position<-"PG"
```
# For Richard Jefferson (SF)
```{r,echo = FALSE}
jefferson<-filter(finals,player=="Richard Jefferson")

density_made<-matrix(nrow=47,ncol=50)
density_missed<-matrix(nrow=47,ncol=50)
density_pctg<-matrix(nrow=47,ncol=50)

for(i in -25:24){
  square_feet_x<-filter(jefferson,converted_x>i & converted_x<=i+1)
  ## subset(jefferson,(converted_x>-25 & converted_x<=-24))
  for(j in -47:-1){
    square_feet<-filter(square_feet_x,converted_y>j & converted_y<=j+1)
    ## subset (square_feet_x,(converted_y>-47 & converted_y<=-46))
    a<-nrow(subset(square_feet,square_feet$result=="made"))
    density_made[j+48,i+26]<-a
    b<-nrow(subset(square_feet,square_feet$result=="missed"))
    density_missed[j+48,i+26]<-b
    density_pctg[j+48,i+26]<-a/(a+b)
  }
}
## density_made
dma<-as.data.frame(density_made)
colnames(dma)<-seq(from=-24.5,to=24.5,by=1)
rownames(dma)<-seq(from=-46.5,to=-0.5,by=1)
dma<-as.matrix(dma)
## density_missed
dmi<-as.data.frame(density_missed)
colnames(dmi)<-seq(from=-24.5,to=24.5,by=1)
rownames(dmi)<-seq(from=-46.5,to=-0.5,by=1)
dmi<-as.matrix(dmi)
## density_percentage
dpctg<-as.data.frame(density_pctg)
colnames(dpctg)<-seq(from=-24.5,to=24.5,by=1)
rownames(dpctg)<-seq(from=-46.5,to=-0.5,by=1)
dpctg<-as.matrix(dpctg)
```
## On 1*1 grids
```{r,echo = FALSE}
dpctgdf<-as.data.frame(dpctg)
jefferson12<-dpctgdf
jefferson12$converted_y<-rownames(jefferson12)
jefferson123<-gather(jefferson12,"converted_x","PCTG",1:50)
jefferson123[,c(1,2)]<-jefferson123[,c(2,1)]
colnames(jefferson123)<-colnames(jefferson123[c(2,1,3)])
jefferson123<-as.data.frame(jefferson123)
jefferson1234<-filter(jefferson123,is.nan(PCTG)==FALSE)
jefferson1234$converted_x<-as.numeric(jefferson1234$converted_x) # With correction
jefferson1234$converted_y<-as.numeric(jefferson1234$converted_y) # With correction
jefferson1234$PCTG<-as.numeric(jefferson1234$PCTG)


dmidf<-as.data.frame(dmi)
jefferson22<-dmidf
jefferson22$converted_y<-rownames(jefferson22)
jefferson223<-gather(jefferson22,"converted_x","nmissed",1:50)
jefferson2234<-merge(jefferson1234,jefferson223,by=c("converted_x","converted_y"))

dmadf<-as.data.frame(dma)
jefferson32<-dmadf
jefferson32$converted_y<-rownames(jefferson32)
jefferson323<-gather(jefferson32,"converted_x","nmade",1:50)
jefferson3234<-merge(jefferson2234,jefferson323,by=c("converted_x","converted_y"))
jefferson3234$Shots<-jefferson3234$nmade+jefferson3234$nmissed
jefferson3234$nnormalized<-jefferson3234$Shots/max(jefferson3234$Shots)
jefferson3234$Distance<-sqrt((jefferson3234$converted_x)^2+(jefferson3234$converted_y+41.75)^2)
jefferson3234$Name<-"Richard Jefferson"
jefferson3234$Position<-"PG"
```
## Rbind 1
```{r}
allplayer3234<-rbind(frye3234,shumpert3234,smith3234,love3234,irving3234,james3234,dellavedova3234,jefferson3234,mozgov3234,thompson3234)
indexsweet<-which(allplayer3234$PCTG>=0.5)
indexnonsweet<-which(allplayer3234$PCTG<=0.4)
allplayersweet<-allplayer3234[indexsweet,]
allplayernonsweet<-allplayer3234[indexnonsweet,]
allplayersweet<-filter(allplayersweet)
allplayernonsweet<-filter(allplayernonsweet)
max(allplayersweet$Shots)
max(allplayernonsweet$Shots)
0.4/max(allplayersweet$PCTG)
0.5/max(allplayersweet$PCTG)
0.4/(max(allplayersweet$PCTG)+min(allplayernonsweet$PCTG))
0.5/(max(allplayersweet$PCTG)+min(allplayernonsweet$PCTG))

g4<-ggplot()+geom_point(data=allplayersweet,aes(x=converted_x,y=converted_y,color=PCTG,size=Shots,shape=Position))+geom_point(data=allplayernonsweet,aes(x=converted_x,y=converted_y,color=PCTG,size=Shots,shape=Position))+scale_color_gradientn(colours=c("black","grey","white","orange","red"),values=c(0,0.40,0.45,0.50,1),breaks=c(0.4,0.5))+
  # geom_point(shape=0)+
  geom_path(data=data.frame(x=c(-25,-25,25,25,-25),y=c(-47,0,0,-47,-47)),aes(x=x,y=y))+ ## Rim
  geom_path(data=data.frame(x=c(-25,25),y=c(0,0)),aes(x=x,y=y))+ ## Mid-Line
  ## geom_path(data=data.frame(x=c(-6000:(-1)/1000,1:6000/1000),y=c(sqrt(6^2-c(-6000:(-1)/1000,1:6000/1000)^2))),aes(x=x,y=y))+
  geom_path(data=data.frame(x=c(-6000:(-1)/1000,1:6000/1000),y=-c(sqrt(6^2-c(-6000:(-1)/1000,1:6000/1000)^2))),aes(x=x,y=y))+ ## The half-court arc
  geom_path(data=data.frame(x=c(-6000:(-1)/1000,1:6000/1000),y=-c(28-sqrt(6^2-c(-6000:(-1)/1000,1:6000/1000)^2))),aes(x=x,y=y))+ 
  geom_path(data=data.frame(x=c(-6000:(-1)/1000,1:6000/1000),y=-c(28+sqrt(6^2-c(-6000:(-1)/1000,1:6000/1000)^2))),aes(x=x,y=y),linetype='dashed')+ ## The free-throw arc
  geom_path(data=data.frame(x=-c(-8,-8,8,8,-8),y=-c(47,28,28,47,47)),aes(x=x,y=y))+ ## The box
  geom_path(data=data.frame(x=c(-6,-6,6,6,-6),y=-c(47,28,28,47,47)),aes(x=x,y=y))+ ## The inner box
  geom_path(data=data.frame(x=c(-4000:(-1)/1000,1:4000/1000),y=-c(41.25-sqrt(4^2-c(-4000:(-1)/1000,1:4000/1000)^2))),aes(x=x,y=y))+ ## The 3-seconds area
  geom_path(data=data.frame(x=c(-750:(-1)/1000,1:750/1000,750:1/1000,-1:-750/1000),y=-c(c(41.75+sqrt(0.75^2-c(-750:(-1)/1000,1:750/1000)^2)),c(41.75-sqrt(0.75^2-c(750:1/1000,-1:-750/1000)^2)))),aes(x=x,y=y))+ ## The 3-seconds area circle
  geom_path(data=data.frame(x=c(-3,3),y=-c(43,43)),lineend='butt',aes(x=x,y=y))+ ## The hoop
  geom_path(data=data.frame(x=c(-22,-22,-22000:(-1)/1000,1:22000/1000,22,22),y=-c(47,47-169/12,41.75-sqrt(23.75^2-c(-22000:(-1)/1000,1:22000/1000)^2),47-169/12,47)),aes(x=x,y=y))+ ## The 3 pt line
  coord_fixed()+ggtitle("Sweet Spots for Cleveland Cavaliers 1 sqft")+scale_size_continuous(limits=c(0,70),breaks=c(10,25,70))+theme_void(base_size =9) +
  theme(plot.title = element_text(hjust = 0.5))
g4
```