w---
title: "Heat_Maps_Fantasy_Team"
author: "Minjie Xia, David Jeong, Alex Huo, Ignat Kulinka, Tim Yang"
date: "2017/4/28"
output:
  html_document: default
  pdf_document: default
---
```{r,echo=FALSE}
## PF: Nikola Jokic, Gorgui Dieng
## C: Zaza Pachulia, Karl-Anthony Towns
## SG: CJ McCollum, Victor Oladipo
## PG: Darren Collison, Michael Carter-Williams
## SF: Giannis Antetokounmpo, Omri Casspi
library(tidyverse)
library(readr)
library(stringr)
library(tidyr)
library(SportsAnalytics)
## truncatedss<-read_csv("~/Desktop/SPRING 2017/Academics/STATS 199/Data Sets/truncatedss1415.csv")
## truncatedss<-read_csv("~/Desktop/SPRING 2017/Academics/STATS 199/Data Sets/truncatedss1516.csv")
## truncatedss<-read_csv("~/Desktop/SPRING 2017/Academics/STATS 199/Data Sets/ss.csv")
## X1415plusranking <- read_csv("~/Desktop/SPRING 2017/Academics/STATS 199/Data Sets/1415plusranking.csv")
## X1516plusranking <- read_csv("~/Desktop/SPRING 2017/Academics/STATS 199/Data Sets/1516plusranking.csv")
finals <- read_csv("~/Desktop/UCLA/Spring 2017/STATS 199/STATS 199 Research/Final Report/Final_nbadat.csv")
```
# For Nikola Jokic (PF)
```{r,echo = FALSE}
jokic<-filter(finals,player=="Nikola Jokic")

CLE<-filter(finals,team=="CLE")
CLEplayers<-CLE %>% group_by(player) %>% summarise(n=n())
density_made<-matrix(nrow=47,ncol=50)
density_missed<-matrix(nrow=47,ncol=50)
density_pctg<-matrix(nrow=47,ncol=50)

for(i in -25:24){
  square_feet_x<-filter(jokic,converted_x>i & converted_x<=i+1)
  ## subset(jokic,(converted_x>-25 & converted_x<=-24))
  for(j in -47:-1){
    square_feet<-filter(square_feet_x,converted_y>j & converted_y<=j+1)
    ## subset (square_feet_x,(converted_y>-47 & converted_y<=-46))
    a<-nrow(subset(square_feet,square_feet$result=="made"))
    density_made[j+48,i+26]<-a
    b<-nrow(subset(square_feet,square_feet$result=="missed"))
    density_missed[j+48,i+26]<-b
    density_pctg[j+48,i+26]<-a/(a+b)
  }
}
## density_made
dma<-as.data.frame(density_made)
colnames(dma)<-seq(from=-24.5,to=24.5,by=1)
rownames(dma)<-seq(from=-46.5,to=-0.5,by=1)
dma<-as.matrix(dma)
## density_missed
dmi<-as.data.frame(density_missed)
colnames(dmi)<-seq(from=-24.5,to=24.5,by=1)
rownames(dmi)<-seq(from=-46.5,to=-0.5,by=1)
dmi<-as.matrix(dmi)
## density_percentage
dpctg<-as.data.frame(density_pctg)
colnames(dpctg)<-seq(from=-24.5,to=24.5,by=1)
rownames(dpctg)<-seq(from=-46.5,to=-0.5,by=1)
dpctg<-as.matrix(dpctg)
```
## On 1*1 grids
```{r,echo = FALSE}
dpctgdf<-as.data.frame(dpctg)
jokic12<-dpctgdf
jokic12$converted_y<-rownames(jokic12)
jokic123<-gather(jokic12,"converted_x","PCTG",1:50)
jokic123[,c(1,2)]<-jokic123[,c(2,1)]
colnames(jokic123)<-colnames(jokic123[c(2,1,3)])
jokic123<-as.data.frame(jokic123)
jokic1234<-filter(jokic123,is.nan(PCTG)==FALSE)
jokic1234$converted_x<-as.numeric(jokic1234$converted_x) # With correction
jokic1234$converted_y<-as.numeric(jokic1234$converted_y) # With correction
jokic1234$PCTG<-as.numeric(jokic1234$PCTG)


dmidf<-as.data.frame(dmi)
jokic22<-dmidf
jokic22$converted_y<-rownames(jokic22)
jokic223<-gather(jokic22,"converted_x","nmissed",1:50)
jokic2234<-merge(jokic1234,jokic223,by=c("converted_x","converted_y"))

dmadf<-as.data.frame(dma)
jokic32<-dmadf
jokic32$converted_y<-rownames(jokic32)
jokic323<-gather(jokic32,"converted_x","nmade",1:50)
jokic3234<-merge(jokic2234,jokic323,by=c("converted_x","converted_y"))
jokic3234$Shots<-jokic3234$nmade+jokic3234$nmissed
jokic3234$nnormalized<-jokic3234$Shots/max(jokic3234$Shots)
jokic3234$Distance<-sqrt((jokic3234$converted_x)^2+(jokic3234$converted_y+41.75)^2)
jokic3234$Name<-"Steven jokic"
jokic3234$Position<-"PF"
```
## For Gorgui Dieng (PF)
```{r,echo = FALSE}
dieng<-filter(finals,player=="Gorgui Dieng")

density_made<-matrix(nrow=47,ncol=50)
density_missed<-matrix(nrow=47,ncol=50)
density_pctg<-matrix(nrow=47,ncol=50)

for(i in -25:24){
  square_feet_x<-filter(dieng,converted_x>i & converted_x<=i+1)
  ## subset(dieng,(converted_x>-25 & converted_x<=-24))
  for(j in -47:-1){
    square_feet<-filter(square_feet_x,converted_y>j & converted_y<=j+1)
    ## subset (square_feet_x,(converted_y>-47 & converted_y<=-46))
    a<-nrow(subset(square_feet,square_feet$result=="made"))
    density_made[j+48,i+26]<-a
    b<-nrow(subset(square_feet,square_feet$result=="missed"))
    density_missed[j+48,i+26]<-b
    density_pctg[j+48,i+26]<-a/(a+b)
  }
}
## density_made
dma<-as.data.frame(density_made)
colnames(dma)<-seq(from=-24.5,to=24.5,by=1)
rownames(dma)<-seq(from=-46.5,to=-0.5,by=1)
dma<-as.matrix(dma)
## density_missed
dmi<-as.data.frame(density_missed)
colnames(dmi)<-seq(from=-24.5,to=24.5,by=1)
rownames(dmi)<-seq(from=-46.5,to=-0.5,by=1)
dmi<-as.matrix(dmi)
## density_percentage
dpctg<-as.data.frame(density_pctg)
colnames(dpctg)<-seq(from=-24.5,to=24.5,by=1)
rownames(dpctg)<-seq(from=-46.5,to=-0.5,by=1)
dpctg<-as.matrix(dpctg)
```
## On 1*1 grids
```{r,echo = FALSE}
dpctgdf<-as.data.frame(dpctg)
dieng12<-dpctgdf
dieng12$converted_y<-rownames(dieng12)
dieng123<-gather(dieng12,"converted_x","PCTG",1:50)
dieng123[,c(1,2)]<-dieng123[,c(2,1)]
colnames(dieng123)<-colnames(dieng123[c(2,1,3)])
dieng123<-as.data.frame(dieng123)
dieng1234<-filter(dieng123,is.nan(PCTG)==FALSE)
dieng1234$converted_x<-as.numeric(dieng1234$converted_x) # With correction
dieng1234$converted_y<-as.numeric(dieng1234$converted_y) # With correction
dieng1234$PCTG<-as.numeric(dieng1234$PCTG)


dmidf<-as.data.frame(dmi)
dieng22<-dmidf
dieng22$converted_y<-rownames(dieng22)
dieng223<-gather(dieng22,"converted_x","nmissed",1:50)
dieng2234<-merge(dieng1234,dieng223,by=c("converted_x","converted_y"))

dmadf<-as.data.frame(dma)
dieng32<-dmadf
dieng32$converted_y<-rownames(dieng32)
dieng323<-gather(dieng32,"converted_x","nmade",1:50)
dieng3234<-merge(dieng2234,dieng323,by=c("converted_x","converted_y"))
dieng3234$Shots<-dieng3234$nmade+dieng3234$nmissed
dieng3234$nnormalized<-dieng3234$Shots/max(dieng3234$Shots)
dieng3234$Distance<-sqrt((dieng3234$converted_x)^2+(dieng3234$converted_y+41.75)^2)
dieng3234$Name<-"Gorgui Dieng"
dieng3234$Position<-"PF"
```
# For Zaza Pachulia (C)
```{r,echo = FALSE}
pachulia<-filter(finals,player=="Zaza Pachulia")

density_made<-matrix(nrow=47,ncol=50)
density_missed<-matrix(nrow=47,ncol=50)
density_pctg<-matrix(nrow=47,ncol=50)

for(i in -25:24){
  square_feet_x<-filter(pachulia,converted_x>i & converted_x<=i+1)
  ## subset(pachulia,(converted_x>-25 & converted_x<=-24))
  for(j in -47:-1){
    square_feet<-filter(square_feet_x,converted_y>j & converted_y<=j+1)
    ## subset (square_feet_x,(converted_y>-47 & converted_y<=-46))
    a<-nrow(subset(square_feet,square_feet$result=="made"))
    density_made[j+48,i+26]<-a
    b<-nrow(subset(square_feet,square_feet$result=="missed"))
    density_missed[j+48,i+26]<-b
    density_pctg[j+48,i+26]<-a/(a+b)
  }
}
## density_made
dma<-as.data.frame(density_made)
colnames(dma)<-seq(from=-24.5,to=24.5,by=1)
rownames(dma)<-seq(from=-46.5,to=-0.5,by=1)
dma<-as.matrix(dma)
## density_missed
dmi<-as.data.frame(density_missed)
colnames(dmi)<-seq(from=-24.5,to=24.5,by=1)
rownames(dmi)<-seq(from=-46.5,to=-0.5,by=1)
dmi<-as.matrix(dmi)
## density_percentage
dpctg<-as.data.frame(density_pctg)
colnames(dpctg)<-seq(from=-24.5,to=24.5,by=1)
rownames(dpctg)<-seq(from=-46.5,to=-0.5,by=1)
dpctg<-as.matrix(dpctg)
```
## On 1*1 grids
```{r,echo = FALSE}
dpctgdf<-as.data.frame(dpctg)
pachulia12<-dpctgdf
pachulia12$converted_y<-rownames(pachulia12)
pachulia123<-gather(pachulia12,"converted_x","PCTG",1:50)
pachulia123[,c(1,2)]<-pachulia123[,c(2,1)]
colnames(pachulia123)<-colnames(pachulia123[c(2,1,3)])
pachulia123<-as.data.frame(pachulia123)
pachulia1234<-filter(pachulia123,is.nan(PCTG)==FALSE)
pachulia1234$converted_x<-as.numeric(pachulia1234$converted_x) # With correction
pachulia1234$converted_y<-as.numeric(pachulia1234$converted_y) # With correction
pachulia1234$PCTG<-as.numeric(pachulia1234$PCTG)


dmidf<-as.data.frame(dmi)
pachulia22<-dmidf
pachulia22$converted_y<-rownames(pachulia22)
pachulia223<-gather(pachulia22,"converted_x","nmissed",1:50)
pachulia2234<-merge(pachulia1234,pachulia223,by=c("converted_x","converted_y"))

dmadf<-as.data.frame(dma)
pachulia32<-dmadf
pachulia32$converted_y<-rownames(pachulia32)
pachulia323<-gather(pachulia32,"converted_x","nmade",1:50)
pachulia3234<-merge(pachulia2234,pachulia323,by=c("converted_x","converted_y"))
pachulia3234$Shots<-pachulia3234$nmade+pachulia3234$nmissed
pachulia3234$nnormalized<-pachulia3234$Shots/max(pachulia3234$Shots)
pachulia3234$Distance<-sqrt((pachulia3234$converted_x)^2+(pachulia3234$converted_y+41.75)^2)
pachulia3234$Name<-"Zaza Pachulia"
pachulia3234$Position<-"C"
```
# For Karl-Anthony Towns (C)
```{r,echo = FALSE}
towns<-filter(finals,player=="Karl-Anthony Towns")

density_made<-matrix(nrow=47,ncol=50)
density_missed<-matrix(nrow=47,ncol=50)
density_pctg<-matrix(nrow=47,ncol=50)

for(i in -25:24){
  square_feet_x<-filter(towns,converted_x>i & converted_x<=i+1)
  ## subset(towns,(converted_x>-25 & converted_x<=-24))
  for(j in -47:-1){
    square_feet<-filter(square_feet_x,converted_y>j & converted_y<=j+1)
    ## subset (square_feet_x,(converted_y>-47 & converted_y<=-46))
    a<-nrow(subset(square_feet,square_feet$result=="made"))
    density_made[j+48,i+26]<-a
    b<-nrow(subset(square_feet,square_feet$result=="missed"))
    density_missed[j+48,i+26]<-b
    density_pctg[j+48,i+26]<-a/(a+b)
  }
}
## density_made
dma<-as.data.frame(density_made)
colnames(dma)<-seq(from=-24.5,to=24.5,by=1)
rownames(dma)<-seq(from=-46.5,to=-0.5,by=1)
dma<-as.matrix(dma)
## density_missed
dmi<-as.data.frame(density_missed)
colnames(dmi)<-seq(from=-24.5,to=24.5,by=1)
rownames(dmi)<-seq(from=-46.5,to=-0.5,by=1)
dmi<-as.matrix(dmi)
## density_percentage
dpctg<-as.data.frame(density_pctg)
colnames(dpctg)<-seq(from=-24.5,to=24.5,by=1)
rownames(dpctg)<-seq(from=-46.5,to=-0.5,by=1)
dpctg<-as.matrix(dpctg)
```
## On 1*1 grids
```{r,echo = FALSE}
dpctgdf<-as.data.frame(dpctg)
towns12<-dpctgdf
towns12$converted_y<-rownames(towns12)
towns123<-gather(towns12,"converted_x","PCTG",1:50)
towns123[,c(1,2)]<-towns123[,c(2,1)]
colnames(towns123)<-colnames(towns123[c(2,1,3)])
towns123<-as.data.frame(towns123)
towns1234<-filter(towns123,is.nan(PCTG)==FALSE)
towns1234$converted_x<-as.numeric(towns1234$converted_x) # With correction
towns1234$converted_y<-as.numeric(towns1234$converted_y) # With correction
towns1234$PCTG<-as.numeric(towns1234$PCTG)


dmidf<-as.data.frame(dmi)
towns22<-dmidf
towns22$converted_y<-rownames(towns22)
towns223<-gather(towns22,"converted_x","nmissed",1:50)
towns2234<-merge(towns1234,towns223,by=c("converted_x","converted_y"))

dmadf<-as.data.frame(dma)
towns32<-dmadf
towns32$converted_y<-rownames(towns32)
towns323<-gather(towns32,"converted_x","nmade",1:50)
towns3234<-merge(towns2234,towns323,by=c("converted_x","converted_y"))
towns3234$Shots<-towns3234$nmade+towns3234$nmissed
towns3234$nnormalized<-towns3234$Shots/max(towns3234$Shots)
towns3234$Distance<-sqrt((towns3234$converted_x)^2+(towns3234$converted_y+41.75)^2)
towns3234$Name<-"Karl-Anthony Towns"
towns3234$Position<-"C"
```
# For CJ McCollum (SG)
```{r,echo = FALSE}
mccollum<-filter(finals,player=="CJ McCollum")

density_made<-matrix(nrow=47,ncol=50)
density_missed<-matrix(nrow=47,ncol=50)
density_pctg<-matrix(nrow=47,ncol=50)

for(i in -25:24){
  square_feet_x<-filter(mccollum,converted_x>i & converted_x<=i+1)
  ## subset(mccollum,(converted_x>-25 & converted_x<=-24))
  for(j in -47:-1){
    square_feet<-filter(square_feet_x,converted_y>j & converted_y<=j+1)
    ## subset (square_feet_x,(converted_y>-47 & converted_y<=-46))
    a<-nrow(subset(square_feet,square_feet$result=="made"))
    density_made[j+48,i+26]<-a
    b<-nrow(subset(square_feet,square_feet$result=="missed"))
    density_missed[j+48,i+26]<-b
    density_pctg[j+48,i+26]<-a/(a+b)
  }
}
## density_made
dma<-as.data.frame(density_made)
colnames(dma)<-seq(from=-24.5,to=24.5,by=1)
rownames(dma)<-seq(from=-46.5,to=-0.5,by=1)
dma<-as.matrix(dma)
## density_missed
dmi<-as.data.frame(density_missed)
colnames(dmi)<-seq(from=-24.5,to=24.5,by=1)
rownames(dmi)<-seq(from=-46.5,to=-0.5,by=1)
dmi<-as.matrix(dmi)
## density_percentage
dpctg<-as.data.frame(density_pctg)
colnames(dpctg)<-seq(from=-24.5,to=24.5,by=1)
rownames(dpctg)<-seq(from=-46.5,to=-0.5,by=1)
dpctg<-as.matrix(dpctg)
```
## On 1*1 grids
```{r,echo = FALSE}
dpctgdf<-as.data.frame(dpctg)
mccollum12<-dpctgdf
mccollum12$converted_y<-rownames(mccollum12)
mccollum123<-gather(mccollum12,"converted_x","PCTG",1:50)
mccollum123[,c(1,2)]<-mccollum123[,c(2,1)]
colnames(mccollum123)<-colnames(mccollum123[c(2,1,3)])
mccollum123<-as.data.frame(mccollum123)
mccollum1234<-filter(mccollum123,is.nan(PCTG)==FALSE)
mccollum1234$converted_x<-as.numeric(mccollum1234$converted_x) # With correction
mccollum1234$converted_y<-as.numeric(mccollum1234$converted_y) # With correction
mccollum1234$PCTG<-as.numeric(mccollum1234$PCTG)


dmidf<-as.data.frame(dmi)
mccollum22<-dmidf
mccollum22$converted_y<-rownames(mccollum22)
mccollum223<-gather(mccollum22,"converted_x","nmissed",1:50)
mccollum2234<-merge(mccollum1234,mccollum223,by=c("converted_x","converted_y"))

dmadf<-as.data.frame(dma)
mccollum32<-dmadf
mccollum32$converted_y<-rownames(mccollum32)
mccollum323<-gather(mccollum32,"converted_x","nmade",1:50)
mccollum3234<-merge(mccollum2234,mccollum323,by=c("converted_x","converted_y"))
mccollum3234$Shots<-mccollum3234$nmade+mccollum3234$nmissed
mccollum3234$nnormalized<-mccollum3234$Shots/max(mccollum3234$Shots)
mccollum3234$Distance<-sqrt((mccollum3234$converted_x)^2+(mccollum3234$converted_y+41.75)^2)
mccollum3234$Name<-"CJ McCollum"
mccollum3234$Position<-"SG"
```
# For Victor Oladipo (SG)
```{r,echo = FALSE}
oladipo<-filter(finals,player=="Victor Oladipo")

density_made<-matrix(nrow=47,ncol=50)
density_missed<-matrix(nrow=47,ncol=50)
density_pctg<-matrix(nrow=47,ncol=50)

for(i in -25:24){
  square_feet_x<-filter(oladipo,converted_x>i & converted_x<=i+1)
  ## subset(oladipo,(converted_x>-25 & converted_x<=-24))
  for(j in -47:-1){
    square_feet<-filter(square_feet_x,converted_y>j & converted_y<=j+1)
    ## subset (square_feet_x,(converted_y>-47 & converted_y<=-46))
    a<-nrow(subset(square_feet,square_feet$result=="made"))
    density_made[j+48,i+26]<-a
    b<-nrow(subset(square_feet,square_feet$result=="missed"))
    density_missed[j+48,i+26]<-b
    density_pctg[j+48,i+26]<-a/(a+b)
  }
}
## density_made
dma<-as.data.frame(density_made)
colnames(dma)<-seq(from=-24.5,to=24.5,by=1)
rownames(dma)<-seq(from=-46.5,to=-0.5,by=1)
dma<-as.matrix(dma)
## density_missed
dmi<-as.data.frame(density_missed)
colnames(dmi)<-seq(from=-24.5,to=24.5,by=1)
rownames(dmi)<-seq(from=-46.5,to=-0.5,by=1)
dmi<-as.matrix(dmi)
## density_percentage
dpctg<-as.data.frame(density_pctg)
colnames(dpctg)<-seq(from=-24.5,to=24.5,by=1)
rownames(dpctg)<-seq(from=-46.5,to=-0.5,by=1)
dpctg<-as.matrix(dpctg)
```
## On 1*1 grids
```{r,echo = FALSE}
dpctgdf<-as.data.frame(dpctg)
oladipo12<-dpctgdf
oladipo12$converted_y<-rownames(oladipo12)
oladipo123<-gather(oladipo12,"converted_x","PCTG",1:50)
oladipo123[,c(1,2)]<-oladipo123[,c(2,1)]
colnames(oladipo123)<-colnames(oladipo123[c(2,1,3)])
oladipo123<-as.data.frame(oladipo123)
oladipo1234<-filter(oladipo123,is.nan(PCTG)==FALSE)
oladipo1234$converted_x<-as.numeric(oladipo1234$converted_x) # With correction
oladipo1234$converted_y<-as.numeric(oladipo1234$converted_y) # With correction
oladipo1234$PCTG<-as.numeric(oladipo1234$PCTG)


dmidf<-as.data.frame(dmi)
oladipo22<-dmidf
oladipo22$converted_y<-rownames(oladipo22)
oladipo223<-gather(oladipo22,"converted_x","nmissed",1:50)
oladipo2234<-merge(oladipo1234,oladipo223,by=c("converted_x","converted_y"))

dmadf<-as.data.frame(dma)
oladipo32<-dmadf
oladipo32$converted_y<-rownames(oladipo32)
oladipo323<-gather(oladipo32,"converted_x","nmade",1:50)
oladipo3234<-merge(oladipo2234,oladipo323,by=c("converted_x","converted_y"))
oladipo3234$Shots<-oladipo3234$nmade+oladipo3234$nmissed
oladipo3234$nnormalized<-oladipo3234$Shots/max(oladipo3234$Shots)
oladipo3234$Distance<-sqrt((oladipo3234$converted_x)^2+(oladipo3234$converted_y+41.75)^2)
oladipo3234$Name<-"Victor Oladipo"
oladipo3234$Position<-"SG"
```
# For Darren Collison (PG)
```{r,echo = FALSE}
collison<-filter(finals,player=="Darren Collison")

density_made<-matrix(nrow=47,ncol=50)
density_missed<-matrix(nrow=47,ncol=50)
density_pctg<-matrix(nrow=47,ncol=50)

for(i in -25:24){
  square_feet_x<-filter(collison,converted_x>i & converted_x<=i+1)
  ## subset(collison,(converted_x>-25 & converted_x<=-24))
  for(j in -47:-1){
    square_feet<-filter(square_feet_x,converted_y>j & converted_y<=j+1)
    ## subset (square_feet_x,(converted_y>-47 & converted_y<=-46))
    a<-nrow(subset(square_feet,square_feet$result=="made"))
    density_made[j+48,i+26]<-a
    b<-nrow(subset(square_feet,square_feet$result=="missed"))
    density_missed[j+48,i+26]<-b
    density_pctg[j+48,i+26]<-a/(a+b)
  }
}
## density_made
dma<-as.data.frame(density_made)
colnames(dma)<-seq(from=-24.5,to=24.5,by=1)
rownames(dma)<-seq(from=-46.5,to=-0.5,by=1)
dma<-as.matrix(dma)
## density_missed
dmi<-as.data.frame(density_missed)
colnames(dmi)<-seq(from=-24.5,to=24.5,by=1)
rownames(dmi)<-seq(from=-46.5,to=-0.5,by=1)
dmi<-as.matrix(dmi)
## density_percentage
dpctg<-as.data.frame(density_pctg)
colnames(dpctg)<-seq(from=-24.5,to=24.5,by=1)
rownames(dpctg)<-seq(from=-46.5,to=-0.5,by=1)
dpctg<-as.matrix(dpctg)
```
## On 1*1 grids
```{r,echo = FALSE}
dpctgdf<-as.data.frame(dpctg)
collison12<-dpctgdf
collison12$converted_y<-rownames(collison12)
collison123<-gather(collison12,"converted_x","PCTG",1:50)
collison123[,c(1,2)]<-collison123[,c(2,1)]
colnames(collison123)<-colnames(collison123[c(2,1,3)])
collison123<-as.data.frame(collison123)
collison1234<-filter(collison123,is.nan(PCTG)==FALSE)
collison1234$converted_x<-as.numeric(collison1234$converted_x) # With correction
collison1234$converted_y<-as.numeric(collison1234$converted_y) # With correction
collison1234$PCTG<-as.numeric(collison1234$PCTG)


dmidf<-as.data.frame(dmi)
collison22<-dmidf
collison22$converted_y<-rownames(collison22)
collison223<-gather(collison22,"converted_x","nmissed",1:50)
collison2234<-merge(collison1234,collison223,by=c("converted_x","converted_y"))

dmadf<-as.data.frame(dma)
collison32<-dmadf
collison32$converted_y<-rownames(collison32)
collison323<-gather(collison32,"converted_x","nmade",1:50)
collison3234<-merge(collison2234,collison323,by=c("converted_x","converted_y"))
collison3234$Shots<-collison3234$nmade+collison3234$nmissed
collison3234$nnormalized<-collison3234$Shots/max(collison3234$Shots)
collison3234$Distance<-sqrt((collison3234$converted_x)^2+(collison3234$converted_y+41.75)^2)
collison3234$Name<-"Darren Collison"
collison3234$Position<-"PG"
```
# For Michael Carter-Williams (PG)
```{r,echo = FALSE}
carterwilliams<-filter(finals,player=="Michael Carter-Williams")

density_made<-matrix(nrow=47,ncol=50)
density_missed<-matrix(nrow=47,ncol=50)
density_pctg<-matrix(nrow=47,ncol=50)

for(i in -25:24){
  square_feet_x<-filter(carterwilliams,converted_x>i & converted_x<=i+1)
  ## subset(carterwilliams,(converted_x>-25 & converted_x<=-24))
  for(j in -47:-1){
    square_feet<-filter(square_feet_x,converted_y>j & converted_y<=j+1)
    ## subset (square_feet_x,(converted_y>-47 & converted_y<=-46))
    a<-nrow(subset(square_feet,square_feet$result=="made"))
    density_made[j+48,i+26]<-a
    b<-nrow(subset(square_feet,square_feet$result=="missed"))
    density_missed[j+48,i+26]<-b
    density_pctg[j+48,i+26]<-a/(a+b)
  }
}
## density_made
dma<-as.data.frame(density_made)
colnames(dma)<-seq(from=-24.5,to=24.5,by=1)
rownames(dma)<-seq(from=-46.5,to=-0.5,by=1)
dma<-as.matrix(dma)
## density_missed
dmi<-as.data.frame(density_missed)
colnames(dmi)<-seq(from=-24.5,to=24.5,by=1)
rownames(dmi)<-seq(from=-46.5,to=-0.5,by=1)
dmi<-as.matrix(dmi)
## density_percentage
dpctg<-as.data.frame(density_pctg)
colnames(dpctg)<-seq(from=-24.5,to=24.5,by=1)
rownames(dpctg)<-seq(from=-46.5,to=-0.5,by=1)
dpctg<-as.matrix(dpctg)
```
## On 1*1 grids
```{r,echo = FALSE}
dpctgdf<-as.data.frame(dpctg)
carterwilliams12<-dpctgdf
carterwilliams12$converted_y<-rownames(carterwilliams12)
carterwilliams123<-gather(carterwilliams12,"converted_x","PCTG",1:50)
carterwilliams123[,c(1,2)]<-carterwilliams123[,c(2,1)]
colnames(carterwilliams123)<-colnames(carterwilliams123[c(2,1,3)])
carterwilliams123<-as.data.frame(carterwilliams123)
carterwilliams1234<-filter(carterwilliams123,is.nan(PCTG)==FALSE)
carterwilliams1234$converted_x<-as.numeric(carterwilliams1234$converted_x) # With correction
carterwilliams1234$converted_y<-as.numeric(carterwilliams1234$converted_y) # With correction
carterwilliams1234$PCTG<-as.numeric(carterwilliams1234$PCTG)


dmidf<-as.data.frame(dmi)
carterwilliams22<-dmidf
carterwilliams22$converted_y<-rownames(carterwilliams22)
carterwilliams223<-gather(carterwilliams22,"converted_x","nmissed",1:50)
carterwilliams2234<-merge(carterwilliams1234,carterwilliams223,by=c("converted_x","converted_y"))

dmadf<-as.data.frame(dma)
carterwilliams32<-dmadf
carterwilliams32$converted_y<-rownames(carterwilliams32)
carterwilliams323<-gather(carterwilliams32,"converted_x","nmade",1:50)
carterwilliams3234<-merge(carterwilliams2234,carterwilliams323,by=c("converted_x","converted_y"))
carterwilliams3234$Shots<-carterwilliams3234$nmade+carterwilliams3234$nmissed
carterwilliams3234$nnormalized<-carterwilliams3234$Shots/max(carterwilliams3234$Shots)
carterwilliams3234$Distance<-sqrt((carterwilliams3234$converted_x)^2+(carterwilliams3234$converted_y+41.75)^2)
carterwilliams3234$Name<-"Michael Carter-Williams"
carterwilliams3234$Position<-"PG"
```
# For Giannis Antetokounmpo (SF)
```{r,echo = FALSE}
antetokounmpo<-filter(finals,player=="Giannis Antetokounmpo")

density_made<-matrix(nrow=47,ncol=50)
density_missed<-matrix(nrow=47,ncol=50)
density_pctg<-matrix(nrow=47,ncol=50)

for(i in -25:24){
  square_feet_x<-filter(antetokounmpo,converted_x>i & converted_x<=i+1)
  ## subset(antetokounmpo,(converted_x>-25 & converted_x<=-24))
  for(j in -47:-1){
    square_feet<-filter(square_feet_x,converted_y>j & converted_y<=j+1)
    ## subset (square_feet_x,(converted_y>-47 & converted_y<=-46))
    a<-nrow(subset(square_feet,square_feet$result=="made"))
    density_made[j+48,i+26]<-a
    b<-nrow(subset(square_feet,square_feet$result=="missed"))
    density_missed[j+48,i+26]<-b
    density_pctg[j+48,i+26]<-a/(a+b)
  }
}
## density_made
dma<-as.data.frame(density_made)
colnames(dma)<-seq(from=-24.5,to=24.5,by=1)
rownames(dma)<-seq(from=-46.5,to=-0.5,by=1)
dma<-as.matrix(dma)
## density_missed
dmi<-as.data.frame(density_missed)
colnames(dmi)<-seq(from=-24.5,to=24.5,by=1)
rownames(dmi)<-seq(from=-46.5,to=-0.5,by=1)
dmi<-as.matrix(dmi)
## density_percentage
dpctg<-as.data.frame(density_pctg)
colnames(dpctg)<-seq(from=-24.5,to=24.5,by=1)
rownames(dpctg)<-seq(from=-46.5,to=-0.5,by=1)
dpctg<-as.matrix(dpctg)
```
## On 1*1 grids
```{r,echo = FALSE}
dpctgdf<-as.data.frame(dpctg)
antetokounmpo12<-dpctgdf
antetokounmpo12$converted_y<-rownames(antetokounmpo12)
antetokounmpo123<-gather(antetokounmpo12,"converted_x","PCTG",1:50)
antetokounmpo123[,c(1,2)]<-antetokounmpo123[,c(2,1)]
colnames(antetokounmpo123)<-colnames(antetokounmpo123[c(2,1,3)])
antetokounmpo123<-as.data.frame(antetokounmpo123)
antetokounmpo1234<-filter(antetokounmpo123,is.nan(PCTG)==FALSE)
antetokounmpo1234$converted_x<-as.numeric(antetokounmpo1234$converted_x) # With correction
antetokounmpo1234$converted_y<-as.numeric(antetokounmpo1234$converted_y) # With correction
antetokounmpo1234$PCTG<-as.numeric(antetokounmpo1234$PCTG)


dmidf<-as.data.frame(dmi)
antetokounmpo22<-dmidf
antetokounmpo22$converted_y<-rownames(antetokounmpo22)
antetokounmpo223<-gather(antetokounmpo22,"converted_x","nmissed",1:50)
antetokounmpo2234<-merge(antetokounmpo1234,antetokounmpo223,by=c("converted_x","converted_y"))

dmadf<-as.data.frame(dma)
antetokounmpo32<-dmadf
antetokounmpo32$converted_y<-rownames(antetokounmpo32)
antetokounmpo323<-gather(antetokounmpo32,"converted_x","nmade",1:50)
antetokounmpo3234<-merge(antetokounmpo2234,antetokounmpo323,by=c("converted_x","converted_y"))
antetokounmpo3234$Shots<-antetokounmpo3234$nmade+antetokounmpo3234$nmissed
antetokounmpo3234$nnormalized<-antetokounmpo3234$Shots/max(antetokounmpo3234$Shots)
antetokounmpo3234$Distance<-sqrt((antetokounmpo3234$converted_x)^2+(antetokounmpo3234$converted_y+41.75)^2)
antetokounmpo3234$Name<-"Giannis Antetokounmpo"
antetokounmpo3234$Position<-"SF"
```
# For Omri Casspi (SF)
```{r,echo = FALSE}
casspi<-filter(finals,player=="Omri Casspi")

density_made<-matrix(nrow=47,ncol=50)
density_missed<-matrix(nrow=47,ncol=50)
density_pctg<-matrix(nrow=47,ncol=50)

for(i in -25:24){
  square_feet_x<-filter(casspi,converted_x>i & converted_x<=i+1)
  ## subset(casspi,(converted_x>-25 & converted_x<=-24))
  for(j in -47:-1){
    square_feet<-filter(square_feet_x,converted_y>j & converted_y<=j+1)
    ## subset (square_feet_x,(converted_y>-47 & converted_y<=-46))
    a<-nrow(subset(square_feet,square_feet$result=="made"))
    density_made[j+48,i+26]<-a
    b<-nrow(subset(square_feet,square_feet$result=="missed"))
    density_missed[j+48,i+26]<-b
    density_pctg[j+48,i+26]<-a/(a+b)
  }
}
## density_made
dma<-as.data.frame(density_made)
colnames(dma)<-seq(from=-24.5,to=24.5,by=1)
rownames(dma)<-seq(from=-46.5,to=-0.5,by=1)
dma<-as.matrix(dma)
## density_missed
dmi<-as.data.frame(density_missed)
colnames(dmi)<-seq(from=-24.5,to=24.5,by=1)
rownames(dmi)<-seq(from=-46.5,to=-0.5,by=1)
dmi<-as.matrix(dmi)
## density_percentage
dpctg<-as.data.frame(density_pctg)
colnames(dpctg)<-seq(from=-24.5,to=24.5,by=1)
rownames(dpctg)<-seq(from=-46.5,to=-0.5,by=1)
dpctg<-as.matrix(dpctg)
```
## On 1*1 grids
```{r,echo = FALSE}
dpctgdf<-as.data.frame(dpctg)
casspi12<-dpctgdf
casspi12$converted_y<-rownames(casspi12)
casspi123<-gather(casspi12,"converted_x","PCTG",1:50)
casspi123[,c(1,2)]<-casspi123[,c(2,1)]
colnames(casspi123)<-colnames(casspi123[c(2,1,3)])
casspi123<-as.data.frame(casspi123)
casspi1234<-filter(casspi123,is.nan(PCTG)==FALSE)
casspi1234$converted_x<-as.numeric(casspi1234$converted_x) # With correction
casspi1234$converted_y<-as.numeric(casspi1234$converted_y) # With correction
casspi1234$PCTG<-as.numeric(casspi1234$PCTG)


dmidf<-as.data.frame(dmi)
casspi22<-dmidf
casspi22$converted_y<-rownames(casspi22)
casspi223<-gather(casspi22,"converted_x","nmissed",1:50)
casspi2234<-merge(casspi1234,casspi223,by=c("converted_x","converted_y"))

dmadf<-as.data.frame(dma)
casspi32<-dmadf
casspi32$converted_y<-rownames(casspi32)
casspi323<-gather(casspi32,"converted_x","nmade",1:50)
casspi3234<-merge(casspi2234,casspi323,by=c("converted_x","converted_y"))
casspi3234$Shots<-casspi3234$nmade+casspi3234$nmissed
casspi3234$nnormalized<-casspi3234$Shots/max(casspi3234$Shots)
casspi3234$Distance<-sqrt((casspi3234$converted_x)^2+(casspi3234$converted_y+41.75)^2)
casspi3234$Name<-"Omri Casspi"
casspi3234$Position<-"SF"
```
## Rbind 1
```{r}
allplayer3234<-rbind(jokic3234,dieng3234,pachulia3234,towns3234,mccollum3234,oladipo3234,collison3234,carterwilliams3234,antetokounmpo3234,casspi3234)
indexsweet<-which(allplayer3234$PCTG>=0.5)
indexnonsweet<-which(allplayer3234$PCTG<=0.4)
allplayersweet<-allplayer3234[indexsweet,]
allplayernonsweet<-allplayer3234[indexnonsweet,]
allplayersweet<-filter(allplayersweet)
allplayernonsweet<-filter(allplayernonsweet)
max(allplayersweet$Shots)
max(allplayernonsweet$Shots)
0.4/max(allplayersweet$PCTG)
0.5/max(allplayersweet$PCTG)
0.4/(max(allplayersweet$PCTG)+min(allplayernonsweet$PCTG))
0.5/(max(allplayersweet$PCTG)+min(allplayernonsweet$PCTG))

g4<-ggplot()+geom_point(data=allplayersweet,aes(x=converted_x,y=converted_y,color=PCTG,size=Shots,shape=Position))+geom_point(data=allplayernonsweet,aes(x=converted_x,y=converted_y,color=PCTG,size=Shots,shape=Position))+scale_color_gradientn(colours=c("black","grey","white","orange","red"),values=c(0,0.40,0.45,0.50,1),breaks=c(0.4,0.5))+
  # geom_point(shape=0)+
  geom_path(data=data.frame(x=c(-25,-25,25,25,-25),y=c(-47,0,0,-47,-47)),aes(x=x,y=y))+ ## Rim
  geom_path(data=data.frame(x=c(-25,25),y=c(0,0)),aes(x=x,y=y))+ ## Mid-Line
  ## geom_path(data=data.frame(x=c(-6000:(-1)/1000,1:6000/1000),y=c(sqrt(6^2-c(-6000:(-1)/1000,1:6000/1000)^2))),aes(x=x,y=y))+
  geom_path(data=data.frame(x=c(-6000:(-1)/1000,1:6000/1000),y=-c(sqrt(6^2-c(-6000:(-1)/1000,1:6000/1000)^2))),aes(x=x,y=y))+ ## The half-court arc
  geom_path(data=data.frame(x=c(-6000:(-1)/1000,1:6000/1000),y=-c(28-sqrt(6^2-c(-6000:(-1)/1000,1:6000/1000)^2))),aes(x=x,y=y))+ 
  geom_path(data=data.frame(x=c(-6000:(-1)/1000,1:6000/1000),y=-c(28+sqrt(6^2-c(-6000:(-1)/1000,1:6000/1000)^2))),aes(x=x,y=y),linetype='dashed')+ ## The free-throw arc
  geom_path(data=data.frame(x=-c(-8,-8,8,8,-8),y=-c(47,28,28,47,47)),aes(x=x,y=y))+ ## The box
  geom_path(data=data.frame(x=c(-6,-6,6,6,-6),y=-c(47,28,28,47,47)),aes(x=x,y=y))+ ## The inner box
  geom_path(data=data.frame(x=c(-4000:(-1)/1000,1:4000/1000),y=-c(41.25-sqrt(4^2-c(-4000:(-1)/1000,1:4000/1000)^2))),aes(x=x,y=y))+ ## The 3-seconds area
  geom_path(data=data.frame(x=c(-750:(-1)/1000,1:750/1000,750:1/1000,-1:-750/1000),y=-c(c(41.75+sqrt(0.75^2-c(-750:(-1)/1000,1:750/1000)^2)),c(41.75-sqrt(0.75^2-c(750:1/1000,-1:-750/1000)^2)))),aes(x=x,y=y))+ ## The 3-seconds area circle
  geom_path(data=data.frame(x=c(-3,3),y=-c(43,43)),lineend='butt',aes(x=x,y=y))+ ## The hoop
  geom_path(data=data.frame(x=c(-22,-22,-22000:(-1)/1000,1:22000/1000,22,22),y=-c(47,47-169/12,41.75-sqrt(23.75^2-c(-22000:(-1)/1000,1:22000/1000)^2),47-169/12,47)),aes(x=x,y=y))+ ## The 3 pt line
  coord_fixed()+ggtitle("Sweet and Unsweet Spots for Fantasy Team (1 sqft)")+scale_size_continuous(limits=c(0,70),breaks=c(10,25,70))+theme_void(base_size =9) +
  theme(plot.title = element_text(hjust = 0.5))
g4
```
